### 2010-12-07 doc/tech_doc/xrsl/xrsl-user.tex
Synchronising changes in xrsl related changes

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:executable}\addcontentsline{toc}{subsection}{executable}
  \begin{shaded}
    \xrsl{executable}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(executable=<string>)#\\
    GM input:& for ARC $\leq$ 0.5.25:  \verb#(executable="/bin/echo")#\\
    Example:&\verb#(executable="local_to_job.exe")#\\
  \end{tabular}

@@

  If an executable has to be transferred to the destination site (CE) from some source, it
  has to be specified in the \texttt{inputFiles} list. If it is not specified in \texttt{inputFiles},
  the source is expected to be local to the user (client) and
  will be added as such to the \texttt{inputFiles} list by the UI.

@@

  For ARC $\leq$ 0.5.25, UI created a dummy executable attribute for internal GM use,
  with e.g., "\verb#/bin/echo#" as an argument (unless the
  specified executable itself started with "\verb#/#"). The actual
  executable was transferred by the UI to
  \texttt{arguments}, \texttt{inputFiles} and \texttt{executables} lists
  in the pre-processed xRSL script.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:arguments}\addcontentsline{toc}{subsection}{arguments}
  \begin{shaded}
    \xrsl{arguments}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(arguments=<string> [string] ... )#\\
    GM input:&\verb#(arguments=<executable> <string> [string] ... )#\\
    Example:&\verb#(arguments="10000" $(ATLAS)/input.dat)#\\ %$
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string}&an argument\\
    \hspace*{1cm}&\texttt{executable}&the executable to be run by LRMS, taken by the
    UI from the user-specified \texttt{executable} attribute\\
  \end{tabular}

  For ARC $\leq$ 0.5.25, UI added the name specified in \texttt{executable} to the 
  \texttt{arguments} list in the pre-processed xRSL script.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:inputFiles}\addcontentsline{toc}{subsection}{inputFiles}
  \begin{shaded}
    \xrsl{inputFiles}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{12cm}}
    User input:&\verb#(inputFiles=(<filename> <location>) ... )#\\
    GM input:&\verb#(inputFiles=(<filename> <URL>)#\\
    &\verb#        (<filename> [size][.checksum]) ... )#\\
    Example:&\verb#(inputFiles=("local_to_job" "gsiftp://se1.lu.se/p1/remote_one")#\\
    &\verb#        ("local_to_job.dat" "/scratch/local_to_me.dat")#\\
    &\verb#        ("same_name_as_in_my_current_dir" ""))#\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{filename} & file name, local to the computing element and
    always relative to the session directory\\
    \hspace*{1cm}&\texttt{location} & location of the file (\texttt{gsiftp},
    \texttt{https}, \texttt{ftp}, \texttt{http} URLs, or a path, local
    to the submission node). If void ("", use the quotes!), the input file is taken
    from the submission directory.\\
    \hspace*{1cm}&\texttt{URL} & URL of the file (see Section~\ref{sec:url})\\
    \hspace*{1cm}&\texttt{size} & file size in bytes\\
    \hspace*{1cm}&\texttt{checksum} & file checksum (as returned by \texttt{cksum})\\
  \end{tabular}

  If the list does not contain the standard input file (as specified
  by \texttt{stdin}) and/or the executable file (as specified by
  \texttt{executable} if the given name), the UI appends these files
  to the list. If the \verb#<location># is a URL, it is passed by the
  UI to the GM without changes; if it is a local path (or void, ""),
  the UI converts it to \verb#<size># and \verb#<checksum># and
  uploads those files to the execution cluster.

  \begin{framed}
  Please note that the \texttt{inputFiles} attribute is not meant to
  operate with directories: you must specify a pair
  \verb#("<local_to_job>" "[source]")# for each file.
  \end{framed}

  For ARC $\leq$ 0.5.25, UI added the name specified in \texttt{executable} to the 
  \texttt{inputFiles} list in the pre-processed xRSL script.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:executables}\addcontentsline{toc}{subsection}{executables}
  \begin{shaded}
    \xrsl{executables}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(executables=<string> [string] ...)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(executables="myscript.sh" "myjob.exe")#\\
  \end{tabular}

@@

  If the executable file (as specified in \texttt{executable} and is
  relative to the session directory)  is not listed, it will be added
  to the list by the UI.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:cache}\addcontentsline{toc}{subsection}{cache}
  \begin{shaded}
    \xrsl{cache}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.34, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(cache="yes"|"no")#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(cache="yes")#\\
  \end{tabular}

@@

  \begin{framed}
    Cached files can not be modified by jobs by default. If your job has to 
    modify input files, please specify \texttt{(cache="no")} or use
    \texttt{(readonly="no")} URL option for those files.
  \end{framed}

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:outputFiles}\addcontentsline{toc}{subsection}{outputFiles} 
  \begin{shaded}
    \xrsl{outputFiles}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(outputFiles=(<string> <URL>) ... )#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(outputFiles=("local_to_job.dat" "gsiftp://se1.uo.no/stored.dat")#\\
    &\verb#    ("local_to_job.dat" "rc://rc1.uc.dk/set1/stored_and_indexed.dat")#\\  
    &\verb#    ("local_to_job_dir/" ""))#\\  
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string}& file name, local to the
    \textit{Computing Element (CE)}\index{Computing Element}. If this
    string ends with a backslash "/" and \verb#<URL># is empty, the
    entire directory is being kept at the execution site. If however
    this string ends with a backslash "/" but the \verb#<URL>#
    starts with \texttt{gsiftp} or \texttt{ftp}, the whole directory
    is transfered to the destination.\\
    \hspace*{1cm}&\texttt{URL} & URL of the remote file (see
    Section~\ref{sec:url}); if void ("", use the quotes!), the file is
    kept for manual retrieval.  Note that this can not be a local
    \texttt{file://} URL.\\
  \end{tabular}

@@

  If the list does not contain standard output, standard error
  file names and GM log-files directory name (as specified by \texttt{stdout},
  \texttt{stderr} and \texttt{gmlog}), the UI appends these
  items to the \texttt{outputFiles} list. If the \verb#<URL># is not specified (void,
  "", use the quotes!), files will be kept on SE and should be downloaded 
  by the user via the UI. If specified name of file ends with "/", the 
  entire directory is kept.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:cpuTime}\addcontentsline{toc}{subsection}{cpuTime}
  \begin{shaded}
    \xrsl{cpuTime}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.17\footnote{Was called \texttt{maxCpuTime} for ARC $\leq$ 0.3.16.}, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(cpuTime=<time>)#\\
    GM input:&\verb#(cpuTime=<tttt>)#\\
    Example:&\verb#(cpuTime="240")#\\
  \end{tabular}

  Maximal CPU time request for the job.

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{time} & time (minutes)\\
    \hspace*{1cm}&\texttt{tttt} & time converted by the UI from \texttt{time} to 
    minutes (ARC $\leq$ 0.5.26) or seconds (ARC $\geq$ 0.5.27)\\
  \end{tabular}

  If only number is specified, the time is assumed to be minutes (ARC
  $\leq$ 0.5.26) or seconds (ARC $\geq$ 0.5.27). Otherwise, a free
  format is accepted, i.e., any of the following will be interpreted
  properly (make sure to enclose such strings in quotes!):

@@

  If both \texttt{cpuTime} and \texttt{wallTime} are specified, the UI converts them both to 
  seconds. \texttt{cpuTime} can not be specified together with \texttt{gridTime}
  or \texttt{benchmarks}.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:wallTime}\addcontentsline{toc}{subsection}{wallTime}
  \begin{shaded}
    \xrsl{wallTime}
  \end{shaded}
  \versions{ARC $\geq$ 0.5.27, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(wallTime=<time>)#\\
    GM input:&\verb#(wallTime=<tttt>)#\\
    Example:&\verb#(wallTime="240")#\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{time} & time (minutes)\\
    \hspace*{1cm}&\texttt{tttt} & time converted by the UI from \texttt{time} to seconds\\
  \end{tabular}

  If only number is specified, the time is assumed to be
  seconds. Otherwise, a free format is accepted, i.e., any of the
  following will be interpreted properly (make sure to enclose such
  strings in quotes!):

@@

  If both \texttt{cpuTime} and \texttt{wallTime} are specified, the UI converts them both to 
  seconds. \texttt{wallTime} can not be specified together with \texttt{gridTime}
  or \texttt{benchmarks}. If only \texttt{wallTime} is specified, but not \texttt{cpuTime},
  the corresponding  \texttt{cpuTime} value is evaluated by the UI and added to the job description.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:gridTime}\addcontentsline{toc}{subsection}{gridTime}
  \begin{shaded}
    \xrsl{gridTime}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.31, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(gridTime=<time>)#\\
    GM input:& none\\
    Example:&\verb#(gridTime="2 h")#\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{time} & time (minutes)\\
  \end{tabular}

@@

  \texttt{gridTime} can not be specified together with \texttt{cpuTime}
  or \texttt{wallTime}. If only \texttt{gridTime} is specified, but not \texttt{cpuTime},
  the corresponding  \texttt{cpuTime} value is evaluated by the UI and added to the job description.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:benchmarks}\addcontentsline{toc}{subsection}{benchmarks}
  \begin{shaded}
    \xrsl{benchmarks}
  \end{shaded}
  \versions{ARC $\geq$ 0.5.14, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(benchmarks=(<string> <value> <time>) ... )#\\
    GM input:&\\
    Example:&\verb#(benchmarks=("mybenchmark" "10" "1 hour, 30 minutes"))#\\
  \end{tabular}

@@

  \texttt{benchmarks} can not be specified together with \texttt{cpuTime}
  or \texttt{wallTime}. If only \texttt{benchmarks} is specified, but not \texttt{cpuTime},
  the corresponding  \texttt{cpuTime} value is evaluated by the UI and added to the job description.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:memory}\addcontentsline{toc}{subsection}{memory}
  \begin{shaded}
    \xrsl{memory}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.17\footnote{Was called \texttt{maxMemory} for ARC $\leq$ 0.3.16}, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(memory=<integer>)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(memory>="500")#\\
  \end{tabular}

  Memory required for the job.

@@

  \begin{framed}
    Just like \texttt{cpuTime}, this attribute should be used to
    direct a job to a resource with a sufficient capacity. Jobs
    exceeding this memory limit will most likely be \textbf{terminated}
    by the remote system.
  \end{framed}

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:disk}\addcontentsline{toc}{subsection}{disk}
  \begin{shaded}
    \xrsl{disk}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.17\footnote{Was called \texttt{maxDisk} for ARC $\leq$ 0.3.16}, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(disk=<integer>)#\\
    GM input:&none\\
    Example:&\verb#(disk="500")#\\
  \end{tabular}

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:runTimeEnvironment}\addcontentsline{toc}{subsection}{runTimeEnvironment}
  \begin{shaded}
    \xrsl{runTimeEnvironment}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(runTimeEnvironment=<string>)(runTimeEnvironment=<string>)#\\
    GM input:&For ARC $\leq$ 0.5.39: \verb#(runTimeEnvironment="<string>" "<string>")#\\
    Example:&\verb#(runTimeEnvironment>="APPS/HEP/ATLAS-10.0.1")#\\
  \end{tabular}

@@

  The site to submit the job to will be chosen by the UI among those
  advertising specified runtime environments. Before starting the job,
  the GM will set up environment variables and paths according to
  those requested. Runtime environment names are defined by Virtual 
  Organizations, and tend to be organized in name spaces.

  To request several environments, repeat the attribute string:\\
  \verb#(runTimeEnvironment="ENV1")(runTimeEnvironment="ENV2")# etc.   
  In ARC $\leq$ 0.5.39, before being submitted to the GM, a grouping was done by the UI, such that GM input was,
  e.g., \verb#(runTimeEnvironment="ENV1" "ENV2")#.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:middleware}\addcontentsline{toc}{subsection}{middleware}
  \begin{shaded}
    \xrsl{middleware}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(middleware=<string>)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(middleware="nordugrid-arc-0.5.99")#\\
  \end{tabular}

  Required middleware.

@@

  The site to submit the job to will be chosen by the UI among those
  advertising specified middleware. Usage is identical to that of the
  \texttt{runTimeEnvironment}. Use the "\verb#>=#" operator to
  request a version "equal or higher". Request
  \texttt{(middleware="nordugrid-arc")} defaults to
  \verb#(middleware>="nordugrid-arc-0.0.0.0")#.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:opsys}\addcontentsline{toc}{subsection}{opsys}
  \begin{shaded}
    \xrsl{opsys}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.21, ARC 0.4, ARC 0.5, ARC 0.6}
  \begin{tabular}{lp{13cm}}
    User input:&\verb#(opsys=<string>)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(opsys="FC3")#\\
  \end{tabular}

@@

  The site to submit the job to will be chosen by the UI among those
  advertising specified operating system. Usage is identical to that of
  \texttt{runTimeEnvironment} and \texttt{middleware}. Use the "\verb#>=#" operator to
  request a version "equal or higher".

>>>>

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:executable}\addcontentsline{toc}{subsection}{executable}
  \begin{shaded}
    \xrsl{executable}
  \end{shaded}
  \versions{ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(executable=<string>)#\\
    GM input:& for ARC $\leq$ 0.5.25:  \verb#(executable="/bin/echo")#\\
    Example:&\verb#(executable="local_to_job.exe")#\\
  \end{tabular}

@@

  If an executable has to be transferred to the destination site (CE) from some source, it
  has to be specified in the \texttt{inputFiles} list. If it is not specified in \texttt{inputFiles},
  the source is expected to be local to the user (client) and
  will be added as such to the \texttt{inputFiles} list by the ARC Client.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:arguments}\addcontentsline{toc}{subsection}{arguments}
  \begin{shaded}
    \xrsl{arguments}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(arguments=<string> [string] ... )#\\
    GM input:&\verb#(arguments=<executable> <string> [string] ... )#\\
    Example:&\verb#(arguments="10000" $(ATLAS)/input.dat)#\\ %$
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string}&an argument\\
    \hspace*{1cm}&\texttt{executable}&the executable to be run by LRMS, taken by the
    ARC Client from the user-specified \texttt{executable} attribute\\
  \end{tabular}

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:inputFiles}\addcontentsline{toc}{subsection}{inputFiles}
  \begin{shaded}
    \xrsl{inputFiles}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{12cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(inputFiles=(<filename> <source>) ... )#\\
    GM input:&\verb#(inputFiles=(<filename> <URL>)#\\
    &\verb#        (<filename> [size][.checksum]) ... )#\\
    Example:&\verb#(inputFiles=("local_to_job" "gsiftp://se1.lu.se/p1/remote_one")#\\
    &\verb#        ("local_to_job.dat" "/scratch/local_to_me.dat")#\\
    &\verb#        ("same_name_as_in_my_current_dir" ""))#\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{filename} & destination file name, local to the computing element and
    always relative to the session directory\\
    \hspace*{1cm}&\texttt{source} & source of the file: (\texttt{gsiftp},
    \texttt{https}, \texttt{ftp}, \texttt{http} URLs, or a path, local
    to the submission node). If void ("", use the quotes!), the input file is taken
    from the submission directory.\\
    \hspace*{1cm}&\texttt{URL} & URL of the file (see Section~\ref{sec:url})\\
    \hspace*{1cm}&\texttt{size} & file size in bytes\\
    \hspace*{1cm}&\texttt{checksum} & file checksum (as returned by \texttt{cksum})\\
  \end{tabular}

  \begin{framed}
   ARC Client does not check whether the same destination name is specified for different source locations. Make sure all \texttt{filename} values are different!
  \end{framed}

  If the list does not contain the standard input file (as specified
  by \texttt{stdin}) and/or the executable file (as specified by
  \texttt{executable} if the given name), the ARC Client appends these files
  to the list. If the \verb#<source># is a URL, it is passed by the
  ARC Client to the GM without changes; if it is a local path (or void, ""),
  the ARC Client converts it to \verb#<size># and \verb#<checksum># and
  uploads those files to the execution cluster.

  \begin{framed}
  Please note that the \texttt{inputFiles} attribute is not meant to
  operate with directories, for reasons of access control and checksum verifications. You must specify a pair
  \verb#("<local_to_job>" "<source>")# for each file.
  \end{framed}

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:executables}\addcontentsline{toc}{subsection}{executables}
  \begin{shaded}
    \xrsl{executables}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(executables=<string> [string] ...)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(executables="myscript.sh" "myjob.exe")#\\
  \end{tabular}

@@

  If the executable file (as specified in \texttt{executable} and is
  relative to the session directory)  is not listed, it will be added
  to the list by the ARC Client.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:cache}\addcontentsline{toc}{subsection}{cache}
  \begin{shaded}
    \xrsl{cache}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.34, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(cache="yes"|"no")#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(cache="yes")#\\
  \end{tabular}

@@

  \begin{framed} 
  Cached files can not be modified by jobs by default. If your job has
  to modify input files, please use the \texttt{(readonly="no")} URL
  option for those files. This option does not affect whether or not
  the file is cached.
  \end{framed}

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:outputFiles}\addcontentsline{toc}{subsection}{outputFiles} 
  \begin{shaded}
    \xrsl{outputFiles}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(outputFiles=(<string> <URL>) ... )#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(outputFiles=("local_to_job.dat" "gsiftp://se1.uo.no/stored.dat")#\\
    &\verb#    ("local_to_job.dat" "rc://rc1.uc.dk/set1/stored_and_indexed.dat")#\\  
    &\verb#    ("local_to_job_dir/" ""))#\\  
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{string}& file name, local to the
    \textit{Computing Element (CE)}\index{Computing Element}. If this
    string ends with a backslash "/" and \verb#<URL># is empty, the
    entire directory is being kept at the execution site. If however
    this string ends with a backslash "/" but the \verb#<URL>#
    starts with \texttt{gsiftp} or \texttt{ftp}, the whole directory
    is transfered to the destination.\\
    \hspace*{1cm}&\texttt{URL} & destination URL of the remote file (see
    Section~\ref{sec:url}); if void ("", use the quotes!), the file is
    kept for manual retrieval.  Note that this can not be a local
    \texttt{file://} URL.\\
  \end{tabular}

@@

  If the list does not contain standard output, standard error
  file names and GM log-files directory name (as specified by \texttt{stdout},
  \texttt{stderr} and \texttt{gmlog}), the ARC Client appends these
  items to the \texttt{outputFiles} list. If the \verb#<URL># is not specified (void,
  "", use the quotes!), files will be kept on SE and should be downloaded 
  by the user via the ARC Client. If specified name of file ends with "/", the 
  entire directory is kept.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:cpuTime}\addcontentsline{toc}{subsection}{cpuTime}
  \begin{shaded}
    \xrsl{cpuTime}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.17, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(cpuTime=<time>)#\\
    GM input:&\verb#(cpuTime=<tttt>)#\\
    Example:&\verb#(cpuTime="240")#\\
  \end{tabular}

  Maximal CPU time request for the job. For a multi-processor job, this is a sum over all requested processors.

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{time} & time (in minutes if no unit is specified)\\
    \hspace*{1cm}&\texttt{tttt} & time converted by the ARC Client from \texttt{time} to 
    seconds.\\
  \end{tabular}

  The client converts time specified in the user-side XRSL file to seconds. 
  If no time unit is specified, the client assumes the time given in minutes. 
  Otherwise, a text format is accepted, i.e., any of the following will be interpreted
  properly (make sure to enclose such strings in quotes!):

@@

  If both \texttt{cpuTime} and \texttt{wallTime} are specified, the ARC Client converts them 
  both. \texttt{cpuTime} can not be specified together with \texttt{gridTime}
  or \texttt{benchmarks}.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:wallTime}\addcontentsline{toc}{subsection}{wallTime}
  \begin{shaded}
    \xrsl{wallTime}
  \end{shaded}
  \versions{ARC $\geq$ 0.5.27, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(wallTime=<time>)#\\
    GM input:&\verb#(wallTime=<tttt>)#\\
    Example:&\verb#(wallTime="240")#\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{time} & time (in minutes if no unit is specified)\\
    \hspace*{1cm}&\texttt{tttt} & time converted by the ARC Client to seconds\\
  \end{tabular}

  The client converts time specified in the user-side XRSL file seconds. If no time unit is specified,
  the client assumes the time given in minutes. Otherwise, a text
  format is accepted, i.e., any of the following will be interpreted
  properly (make sure to enclose such strings in quotes!):

@@

  If both \texttt{cpuTime} and \texttt{wallTime} are specified, the ARC Client converts them both.
  \texttt{wallTime} can not be specified together with \texttt{gridTime}
  or \texttt{benchmarks}. If only \texttt{wallTime} is specified, but not \texttt{cpuTime},
  the corresponding  \texttt{cpuTime} value is evaluated by the ARC Client and added to the job description.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:gridTime}\addcontentsline{toc}{subsection}{gridTime}
  \begin{shaded}
    \xrsl{gridTime}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.31, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(gridTime=<time>)#\\
    GM input:& none\\
    Example:&\verb#(gridTime="2 h")#\\
  \end{tabular}

@@

  \begin{tabular}{llp{10cm}}
    \hspace*{1cm}&\texttt{time} & time (in minutes if no unit is specified)\\
  \end{tabular}

@@

  \texttt{gridTime} can not be specified together with \texttt{cpuTime}
  or \texttt{wallTime}. If only \texttt{gridTime} is specified, but not \texttt{cpuTime},
  the corresponding  \texttt{cpuTime} value is evaluated by the ARC Client and added to the job description.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:benchmarks}\addcontentsline{toc}{subsection}{benchmarks}
  \begin{shaded}
    \xrsl{benchmarks}
  \end{shaded}
  \versions{ARC $\geq$ 0.5.14, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(benchmarks=(<string> <value> <time>) ... )#\\
    GM input:&\\
    Example:&\verb#(benchmarks=("mybenchmark" "10" "1 hour, 30 minutes"))#\\
  \end{tabular}

@@

  \texttt{benchmarks} can not be specified together with \texttt{cpuTime}
  or \texttt{wallTime}. If only \texttt{benchmarks} is specified, but not \texttt{cpuTime},
  the corresponding  \texttt{cpuTime} value is evaluated by the ARC Client and added to the job description.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:memory}\addcontentsline{toc}{subsection}{memory}
  \begin{shaded}
    \xrsl{memory}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.17\footnote{Was called \texttt{maxMemory} for ARC $\leq$ 0.3.16}, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(memory=<integer>)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(memory>="500")#\\
  \end{tabular}

  Memory required for the job, per rank.

@@

  \begin{framed}
    Similarly to \texttt{cpuTime}, this attribute should be used to
    direct a job to a resource with a sufficient capacity. Jobs
    exceeding this memory limit will most likely be \textbf{terminated}
    by the remote system.
  \end{framed}

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:disk}\addcontentsline{toc}{subsection}{disk}
  \begin{shaded}
    \xrsl{disk}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.17\footnote{Was called \texttt{maxDisk} for ARC $\leq$ 0.3.16}, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&no\\
    Operators:&\verb#=   !=   >   <   >=   <=#\\
    User input:&\verb#(disk=<integer>)#\\
    GM input:&none\\
    Example:&\verb#(disk="500")#\\
  \end{tabular}

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:runTimeEnvironment}\addcontentsline{toc}{subsection}{runTimeEnvironment}
  \begin{shaded}
    \xrsl{runTimeEnvironment}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&no\\
    Operators:&\verb#=   !=   >   <   >=   <=#\\
    User input:&\verb#(runTimeEnvironment=<string>)(runTimeEnvironment=<string>)#\\
    GM input:&For ARC $\leq$ 0.5.39: \verb#(runTimeEnvironment="<string>" "<string>")#\\
    Example:&\verb#(runTimeEnvironment>="APPS/HEP/ATLAS-10.0.1")#\\
  \end{tabular}

@@

  The site to submit the job to will be chosen by the ARC Client among those
  advertising specified runtime environments. Before starting the job,
  the GM will set up environment variables and paths according to
  those requested. Runtime environment names are defined by Virtual 
  Organizations, and tend to be organized in name spaces.

  To request several environments, repeat the attribute string:\\
  \verb#(runTimeEnvironment="ENV1")(runTimeEnvironment="ENV2")# etc.

@@

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:middleware}\addcontentsline{toc}{subsection}{middleware}
  \begin{shaded}
    \xrsl{middleware}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&no\\
    Operators:&\verb#=   !=   >   <   >=   <=#\\
    User input:&\verb#(middleware=<string>)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(middleware="nordugrid-arc-0.5.99")#\\
  \end{tabular}

  Required middleware version. Make sure to specify full name and version number.

@@

  The site to submit the job to will be chosen by the ARC Client among those
  advertising specified middleware. Usage is identical to that of the
  \texttt{runTimeEnvironment}. Use the "\verb#>=#" operator to
  request a version "equal or higher".% Not true (see bug 1485): Request
  %\texttt{(middleware="nordugrid-arc")} defaults to
  %\verb#(middleware>="nordugrid-arc-0.0.0.0")#.

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:opsys}\addcontentsline{toc}{subsection}{opsys}
  \begin{shaded}
    \xrsl{opsys}
  \end{shaded}
  \versions{ARC $\geq$ 0.3.21, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&no\\
    Operators:&\verb#=   !=   >   <   >=   <=#\\
    User input:&\verb#(opsys=<string>)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(opsys="FC3")#\\
  \end{tabular}

@@

  The site to submit the job to will be chosen by the ARC Client among those
  advertising specified operating system. Usage is identical to that of
  \texttt{runTimeEnvironment} and \texttt{middleware}. Use the "\verb#>=#" operator to
  request a version "equal or higher".

  \hspace*{0.5cm}\phantomsection
  \index{XRSL:attribute:stdin}\addcontentsline{toc}{subsection}{stdin}
  \begin{shaded}
    \xrsl{stdin}
  \end{shaded}
  \versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6, ARC 0.8}
  \begin{tabular}{lp{13cm}}
    Unique:&yes\\
    Operators:&\verb#=#\\
    User input:&\verb#(stdin=<string>)#\\
    GM input:&\verb#-"-#\\
    Example:&\verb#(stdin="myinput.dat")#\\
  \end{tabular}
